Seeing Double: Indications From {\it TESS} and {\it Gaia} That PTFO$\,$8-8695b is Not a Planet

### 2020-04-18 paper/ms.tex
update paper

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia-DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Hertzsprung-Russell diagram of \ptfo\ and late-type members of 25$\,$Ori-1.}
  Members of the 25$\,$Ori-1 group (black circles) were identified by
  \citet{kounkel_apogee2_2018} through clustering on six-dimensional
  Gaia-DR2 and APOGEE-2 data.  The reference
  ``neighborhood'' (gray circles) is the group of at most $10^4$
  randomly selected non-member stars within 5 standard deviations of
  the mean 25$\,$Ori-1 right ascension, declination, and parallax.
  It contains members of the full Orion complex with a wider spread of ages,
  in addition to field interlopers.
  $G$ is the Gaia broadband, $Bp$ is Gaia blue, $Rp$ is Gaia red, and
  $\omega_{\rm as}$ is the parallax in arcseconds.
  The $x$-axis limits have been set to show only K and M dwarf
  members, to accentuate \ptfo's separation from the
  single-star sequence.
	\label{fig:gaia}
	}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.5\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Timing residuals for \ptfob\ from a decade of monitoring.}
		Black points are times of ``dips'', minus the indicated linear
		ephemeris.  The $y$-axis is given in units of phase for the
		short-period signal.  The star shows the binned TESS ephemeris.
		``Dips'' have been observed by \citet{van_eyken_ptf_2012},
		\citet{ciardi_followup_2015}, \citet{yu_tests_2015},
		\citet{raetz_yeti_2016}, \citet{onitsuka_multicolor_2017}, and
		\citet{tanimoto_evidence_2020}.  Certain dips ({\it e.g.}, the one
		at phase 0 in mid-2019) are consistent with noise, and were likely
		reported because something was {\it expected}, rather than
		convincingly {\it observed}.  Horizontal dashed lines are drawn at
		$\pm (P_{\rm \ell} - P_{\rm s})/P_{\rm s}$, highlighting a
    possible observational bias.  The orbital phase observed by TESS
    is consistent with that of \citet{tanimoto_evidence_2020}, and
    quite different from the original phase.
		\label{fig:o_minus_c}
	}
\end{figure}

@@

>>>>

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia-DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Hertzsprung-Russell diagram of \ptfo\ and late-type members of 25$\,$Ori-1.}
  Members of the 25$\,$Ori-1 group (black circles) were identified by
  \citet{kounkel_apogee2_2018} through clustering on six-dimensional
  Gaia-DR2 and APOGEE-2 data.  The reference
  ``neighborhood'' (gray circles) is the group of at most $10^4$
  randomly selected non-member stars within 5 standard deviations of
  the mean 25$\,$Ori-1 right ascension, declination, and parallax.
  It contains members of the full Orion complex with a wider spread of ages,
  in addition to field interlopers.
  $G$ is the Gaia broadband, $Bp$ is Gaia blue, $Rp$ is Gaia red, and
  $\omega_{\rm as}$ is the parallax in arcseconds.
  The $x$-axis limits have been set to show only K and M dwarf
  members, to accentuate \ptfo's separation from the
  single-star sequence.
	\label{fig:gaia}
	}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.5\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Timing residuals for \ptfob\ from a decade of monitoring.}
		Black points are times of ``dips'', minus the indicated linear
		ephemeris.  The $y$-axis is given in units of phase for the
		short-period signal.  The star shows the binned TESS ephemeris.
		``Dips'' have been observed by \citet{van_eyken_ptf_2012},
		\citet{ciardi_followup_2015}, \citet{yu_tests_2015},
		\citet{raetz_yeti_2016}, \citet{onitsuka_multicolor_2017}, and
		\citet{tanimoto_evidence_2020}.  Certain dips ({\it e.g.}, the one
		at phase 0 in mid-2019) are consistent with noise, and were likely
		reported because something was {\it expected}, rather than
		convincingly {\it observed}.  Horizontal dashed lines are drawn at
		$\pm (P_{\rm \ell} - P_{\rm s})/P_{\rm s}$, highlighting a
    possible observational bias.  The orbital phase observed by TESS
    is consistent with that of \citet{tanimoto_evidence_2020}, and
    quite different from the original phase.
		\label{fig:o_minus_c}
	}
\end{figure}

@@

%FIXME: the PTFO lightcurve looks so much worse! Why is it less dense??
\begin{figure*}[hbtp]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf \ptfo\ and its brethren.}
  	Five transient and persistent flux dip stars, selected based on their visual similarity to the short-period signal in \ptfo, are as follows.
  	EPIC 204143627, 1.1250d, dips change depth too
  	EPIC 204321142  Usco flux dip, 0.476d
  	EPIC 204270520  USco flux dip, 0.512d
  	% EPIC 205046529B, 1.8358d, indicates dips can be at weird phases too
  	RIK-210 = EPIC 205483258
 	EPIC 204787516  USco flux dip or possible? EB, 0.487d
 	We found these objects through studies by \citet{stauffer_orbiting_2017}, \citet{david_transient_2017}, and \citet{rebull_usco_2018}.
		\label{fig:brethren}
	}
\end{figure*}

cp ../results/brethren/brethren.pdf f7.pdf
